New insights into the Weddell Sea ecosystem applying a quantitative network approach

### 2023-12-20 Manuscript/Manuscript.Rmd
Final version 19Dec23

The Weddell Sea food web was retrieved from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. In addition to predator-prey interactions, the database contains information on other biological data: mean body mass and length, and movement and metabolic type for each species in the food web. Furthermore, it incorporates information about the interaction itself: type (predacious, herbivorous and detritivorous) and dimension (2 or 3 dimensions according to the predator search space). In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011].

@@

Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding validates the method we used.

@@

The best solution when estimating and evaluating the importance of IS in highly-resolved food webs would probably be to consider more than one methodological approach.Various methodologies have been developed to estimate species IS in food webs, for example, the conceptual framework of the food web energetics [@Gauzens2019] and the inverse model perspective [@Gellner2023]. Although we applied a particular methodology [@Pawar2012], we anticipate that a promising research endeavor would be to compare and contrast our results with those derived from alternative methodologies, which is beyond the scope of our study. Furthermore, a comprehensive review of the diverse methodologies to assign interaction strengths might provide insights into the opportunities and limitations of each approach, guiding the usefulness of each tfor addressing particular questions in future research.

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting with a dashed-line contour the high Antarctic shelf that represents the spatial extent of the food web. Modified from www.soos.aq."}
knitr::include_graphics("Fig.1_StudyMap.jpg")
```

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (median Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$)."}
knitr::include_graphics("Fig4_LinReg_sim.png")
```

>>>>

The Weddell Sea food web was retrieved from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. In addition to predator-prey interactions, the database contains information on other biological data: mean body mass and length, and movement and metabolic type for each species in the food web. Furthermore, it incorporates information about the interaction itself: type (predacious, herbivorous and detritivorous) and dimension (2 or 3 dimensions according to the predator search space). In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011] (Figure A1).

@@

Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding may also be used to validate our method.

@@

The best solution when estimating and evaluating the importance of IS in highly-resolved food webs would probably be to consider more than one methodological approach.Various methodologies have been developed to estimate species IS in food webs, for example, the conceptual framework of the food web energetics [@Gauzens2019] and the inverse model perspective [@Gellner2023]. Although we applied a particular methodology [@Pawar2012], we anticipate that a promising research endeavor would be to compare and contrast our results with those derived from alternative methodologies, which is beyond the scope of our study. Furthermore, a comprehensive review of the diverse methodologies to assign interaction strengths might provide insights into the opportunities and limitations of each approach, guiding the usefulness of each for addressing particular questions in future research.

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector indicating the approximate location of the study area (black star, 74-78ºS) within the high Antarctic shelf. Modified from www.soos.aq."}
knitr::include_graphics("Fig1_StudyMap_ok.png")
```

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (median Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$). Panel (D) shows the distribution of the species' median interaction strength by habitat."}
knitr::include_graphics("Fig4_LinReg_sim.png")
```
